\dppTitle

### 2014-03-07 manuscripts/dpp-msbayes/cover-letter/cover-letter.tex
Updating cover letter for dpp ms.

\signature{Jamie Oaks, Postdoctoral Fellow \\ 
                 Department of Biology \\
                 University of Washington \\ 
                 % Box 351800 \\ 
                 Seattle, WA 98195 \\ 
                 \href{mailto:joaks1@uw.edu}{\texttt{joaks1@uw.edu}} \\ 
                 \href{http://www.phyletica.com}{\texttt{www.phyletica.com}}}
\begin{document}
\begin{letter}{\emph{PLOS Computational Biology} Editorial Board \\
                        1160 Battery Street \\
                        Koshland Building East, Suite 100 \\
                    San Francisco, CA 94111}
\opening{Dear Editor:}
% \raggedright
% I am submitting a manuscript entitled ``An Improved Approximate-Bayesian
% Model-choice Method for Estimating Shared Evolutionary History'' to be
% considered for publication in \highLight{journal here}.
I am submitting a presubmission inquiry regarding a manuscript entitled ``An
Improved Approximate-Bayesian Model-choice Method for Estimating Shared
Evolutionary History'' that I wish to be considered for publication in
\emph{PLOS Computational Biology}.
The field of research is comparative biogeography and Bayesian model choice.

>>>>

\signature{Jamie Oaks, Postdoctoral Fellow \\ 
                 Department of Biology \\
                 University of Washington \\ 
                 % Box 351800 \\ 
                 Seattle, WA 98195, USA \\
                 \href{mailto:joaks1@uw.edu}{\texttt{joaks1@uw.edu}} \\ 
                 \href{http://www.phyletica.com}{\texttt{www.phyletica.com}}}
\begin{document}
\begin{letter}{\emph{BMC Evolutionary Biology} \\
                        BioMed Central \\
                        236 Gray's Inn Road \\
                        London WC1X 8HB \\
                        United Kingdom}
\opening{Dear Editor:}
% \raggedright
I am submitting a manuscript entitled ``An Improved Approximate-Bayesian
Model-choice Method for Estimating Shared Evolutionary History'' to be
considered for publication in \emph{BMC Evolutionary Biology}.
This is a methodological article, and the field of research is comparative
biogeography and Bayesian model choice.
